---
title: "9. Find and Show Slides in a Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{9. Find and Show Slides in a Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

With `write_slides()` you can save a deck into a package. To learn about that function look at the [Creating Slides with write_slides()](ah_write_slides.html)  vignette. How can you check to see if a package contains slides?  If there is one or more deck, how can you see the slides?

## Getting Started

To see if a package has slides use `rUM::find_slides()`. If you want to know if the `rUM` package has slides, you would check with:

`find_slides("rUM")`
 
It will give you a vector containing the names of the slide decks. 
 
```{r}
rUM::find_slides("rUM")
```

To see the slide deck use `rUM::show_slides()`.  For example to see the slide deck called **rUM_the_package** from inside the `rUM` package you would type:

`rUM::show_slides("rUM", "rUM_the_package")`
