---
title: "Creating a Research Project with rUM"
output: rmarkdown::html_vignette
  code-copy: true
vignette: >
  %\VignetteIndexEntry{Make a Research Project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction
This is collection of R things from your friends at UM (the University of Miami).

`rUM` includes:
* A research project template. It creates a new RStudio project that has an analysis R markdown file with tidyverse and conflicted.
* R Markdown templates which include they YAML header and start up blocks that load the tidyverse and conflicted packages.

The plan is to add UM thesis and dissertation Markdown templates.



# Where to order rUM
1. <https://raymondbalise.github.io/rUM/>

1. <https://github.com/RaymondBalise/rUM>

1. or
```r
if (!require("remotes")) installed.packages("remotes")
remotes::install_cran("rUM")

library(rUM)
```


# rUM on the Menu
We would like to create a research project, so we use the `rUM` package. It creates a new RStudio project that has an analysis R markdown file using the `tidyverse` and `conflicted` packages. For more advanced analysis, we can also create R markdown files which use the `tidymodels` package.

## Setup
(To create a research project, see the steps here: <https://raymondbalise.github.io/rUM/>.)



## Session
If you are new to R, ignore this.
```{r}
sessionInfo()
```

