---
title: "1. Using rUM on Posit.Cloud or with Positron"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Using rUM on Posit.Cloud or with Positron}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)

options(rmarkdown.html_vignette.check_title = FALSE)
```

```{css, echo=FALSE}
body > h1 > img {
  position: relative;
  bottom: -30px;
  border: 0px solid rgba(0, 0, 0, 0.1);
 }
```

## Introduction

rUM has many tools to help you write papers and reports efficiently.  They _**will**_ work if you are not working in the RStudio Integrated Development Environment (IDE) on a Mac or Windows but some of the menu options that we show in the other vignettes will not be available.  So you will need to type a line or two into the R console instead of clicking on menu options.  

Here we explain how to use rUM on Posit.Cloud (or other IDEs like Positron). 

## rUM on Posit.Cloud

The other vignettes for `rUM` show you that it integrates with the RStudio IDE menus.  Unfortunately, on Posit.Cloud the **New Project** button does not know about `rUM`. So you will need to type a command to create a new `rUM` based project. Because Posit.Cloud treats each project as its own walled-off environment, you need to tell `rUM` to only work in the current folder/directory.  Most of rUM's functions will do that automatically.  However, `rUM`'s primary function `make_project()` needs you to do this by specifying the location for the project to be `"./"`  (that is UNIX code shorthand that means "in this folder/directory").  Because Posit.Cloud projects have a **project.Rproj** file, you will also need to add the `overwrite = TRUE` option to tell rUM to overwrite the default Posit.Cloud project file.  Here is an example:

```
rUM::make_project("./", overwrite = TRUE)
```

If you want to make a new project that will be a package with a vignette written with Quarto, use code like this:

```
rUM::make_package('./', overwrite = TRUE) 
```

After typing that in the console and pushing return/enter on your keyboard, you will need to confirm that you really want to make a new project.  Choose the option that means **Yes** when RStudio asks you to confirm that you want to overwrite the existing project and namespace files. Say **Yes** when it asks you if you want to quit and **Switch Projects**.  

### Session

If you are new to R, ignore this.

```{r}
sessionInfo()
```
