---
title: "your_title_goes_here"
author: "your_name_goes_here"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    number_sections: false
bibliography: [references.bib, packages.bib]
csl: the-new-england-journal-of-medicine.csl
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
                      ########## set global options ############
    echo = FALSE,     # don't show code
    collapse = TRUE,  # keep code from blocks together (if shown)
    message = TRUE,   # show messages
    warning = TRUE,   # show warnings
    error = TRUE,     # show error messages
    comment = "",     # don't show ## with printed output
    dpi = 100,        # image resolution (typically 300 for publication)
    fig.width = 6.5,  # figure width
    fig.height = 4.0  # figure height
)

# R's default rounding is to show 7 digits. This rounds results to 3 digits.
options(digits = 3)
```

```{r tidyverse-tidymodels, echo=FALSE}
library(conflicted)
suppressPackageStartupMessages(library(tidymodels))
tidymodels_prefer()
suppressPackageStartupMessages(library(tidyverse))

# suppress "`summarise()` has grouped output by " messages
options(dplyr.summarise.inform = FALSE)
```

```{r other-packages}
library(glue)  # for glue()
library(rUM)  # needed for the bibliography to include the package
library(rio)  # for import() 
library(table1)  # for table1() if you want to use it instead of gtsummary

# gtsummary for tbl_summary(), add_n(), add_p(), modify_header(), bold_labels()
suppressPackageStartupMessages(library(gtsummary)) 
```

```{r load-data}
# raw_data <- import("")  # your data file goes inside the ""
```

```{r make-analysis}
# preprocess your data and ultimately make a dataset called analysis

```

# Abstract

# Introduction

# Methods
Analyses were conducted with `r stringr::word(R.Version()$version.string, 1, 3)` with the `tidyverse` (`r packageVersion("tidyverse")`), `rUM` (`r packageVersion("rUM")`), `gtsummary` (`r packageVersion("gtsummary")`) packages used to preprocess and summarize data. [@R-base; @R-tidyverse; @tidyverse2019; @R-rUM; @R-gtsummary]

# Results

```{r table-1}

```

As can be seen in Table \@ref(tab:table-1) or [Table 1](#tab:table-1)

```{r figure1}
#| fig.cap: "Remember figure references begin with #fig:"


```

See Figure \@ref(fig:figure1) or [Figure 1](#fig:figure1)


# Discussion

# References {-}

```{r make-references, include=FALSE}
# automatically create a bib database for loaded R packages & rUM
knitr::write_bib(
  c(
    .packages(),
    "rUM"
  ),
  "packages.bib"
)
```