---
title: "your_title_goes_here"
author: "your_name_goes_here"
date: last-modified
format:
  html:
    embed-resources: true   # true = a single file, false = multiple files
    theme:
      - default
      - custom.scss
knitr:
  opts_chunk:        ########## set global options ############
    collapse: true   # keep code from blocks together (if shown)
    echo: false      # don't show code
    message: true    # show messages
    warning: true    # show warnings
    error: true      # show error messages
    comment: ""      # don't show ## with printed output
    dpi: 100         # image resolution (typically 300 for publication)
    fig-width: 6.5   # figure width
    fig-height: 4.0  # figure height
    R.options:    
      digits: 3      # round to three digits
editor: source
bibliography: [references.bib, packages.bib]
csl: the-new-england-journal-of-medicine.csl
---

```{r load-tidyverse-tidymodels}
#| echo: false

library(conflicted)
suppressPackageStartupMessages(library(tidymodels))
tidymodels_prefer()
suppressPackageStartupMessages(library(tidyverse))

# suppress "`summarise()` has grouped output by " messages
options(dplyr.summarise.inform = FALSE)
```

```{r load-other-packages}
library(glue)  # for glue()
library(rUM)  # needed for the bibliography
library(rio)  # for import() 
library(table1)  # for table1()

# gtsummary for tbl_summary(), add_n(), add_p(), modify_header(), bold_labels()
suppressPackageStartupMessages(library(gtsummary)) 
```

```{r load-data}
# raw_data <- import("")  # your data file goes inside the ""
```

```{r make-analysis}
# preprocess your data and ultimately make a dataset called analysis

```

# Abstract

# Introduction

# Methods

Analyses were conducted with `r stringr::word(R.Version()$version.string, 1, 3)` with the `tidyverse` (`r packageVersion("tidyverse")`), `rUM` (`r packageVersion("rUM")`), `gtsummary` (`r packageVersion("gtsummary")`) packages used to preprocess and summarize data. [@R-base; @R-tidyverse; @tidyverse2019; @R-rUM; @R-gtsummary]

# Results

```{r tbl-table1}
#| tbl-cap: "Cross references to tables use labels for the code chunk starting with tbl-."

```

As can be seen in @tbl-table1 ....

```{r fig-figure-1}
#| fig-cap: "Remember figure labels begin with fig-"

ggplot()
```

As can be seen in @fig-figure-1 ...

# Discussion

# References {.unnumbered}

```{r make-references}
#| include: false

# automatically create a bib database for loaded R packages & rUM
knitr::write_bib(
  c(
    .packages(),
    "rUM"
  ),
  "packages.bib"
)
```