---
title: "Your title goes here"
author: 
  - name: "Your name goes here"
    affiliation:
      - "Department of Public Health Sciences, <br>Division of Biostatistics and Bioinformatics"
date: last-modified
date-format: "MMMM D, YYYY"
format: 
  revealjs:
    theme: [default, slides.scss]
    slideNumber: true
    fontsize: 2em
    html-math-method: mathjax
    slide-number: c/t
    show-slide-number: all
    highlight-style: rstudio_default-light.theme
    title-slide-attributes:
      data-background: "linear-gradient(to right, white 25%, #F47321 25%)"
    pdf-max-pages-per-slide: 1
    pdf-separate-fragments: true
embed-resources: true   # true = a single file, false = multiple files
knitr:
  opts_chunk:      ########## set global options ############
    collapse: true # keep code from blocks together (if shown)
    echo: true     # don't show code
    message: true  # show messages
    warning: true  # show warnings
    error: true    # show error messages
    comment: ""    # don't show ## with printed output
    R.options:   
      digits: 3    # round to three digits
editor_options:
  chunk_output_type: console
editor: source
---
 
# Introduction
 
```{r echo=FALSE}
# Helper packages - need dplyr and ggplot
library(conflicted)
suppressPackageStartupMessages(library(tidymodels))
tidymodels_prefer()
 
suppressPackageStartupMessages(library(tidyverse))

library(knitr)
# library(kableExtra)
```
 


## Using rUM

+ Big Things... You can make:
+ Less Big Things...  You can add:
+ Sorta Big Things... You can:


## Using rUM 

+ Big Things... You can make:
  + A research paper template with `make_project()`
  + A package with a research paper template `make_package()`
+ Less Big Things...  You can add:
+ Sorta Big Things... You can:


## Using rUM 

+ Big Things... You can make:
+ Less Big Things...  You can add:
  + A README file with `write_readme()`
  + A progress notes with `write_notes()`
  + A scss style template with `write_scss()`
  + A manual page for a data set `write_man()`
+ Sorta Big Things... You can:


## Using rUM

+ Big Things... You can make:
+ Less Big Things...  You can add:
+ Sorta Big Things... You can:
  + Add a slide deck with write_slides
    + Into a folder
    + into a package
  + Find slides in a package with `find_slides()`
  + Display slides from a package with `show_slides()`

## rUM Slides Use Themes

Note: The slides use the RStudio color theme by default
```{r}
#| eval: false
#| echo: true
library(rUM)
rUM::find_slides("rUM")
```

You can display all parts of a code bock using {{r}}
```{{r}}
#| eval: false
#| echo: true
library(rUM)
rUM::find_slides("rUM")
```
